---
title: "webResearch analysis results"
date: today
author: webResearch Tool
toc: true
execute: 
  echo: false
format: 
  html:
    embed-resources: true
  docx: default
  odt: default
  pdf: default
params:
  data.file: NA
---

```{r setup}
web_data <- readr::read_rds(file = params$data.file)
library(gtsummary)
library(gt)
library(webResearch)
```

## Introduction

Research should be free and open with easy access for all. The webResearch tool attempts to help lower the bar to participate in contributing to science.

## Methods

Analyses were conducted in R version `r paste(version["major"],version["minor"],sep=".")` using the web-based data analysis tool 'webResearcher' version `r packageVersion("webResearch")`.

## Results

Below is the baseline characteristics plotted.

```{r}
#| label: tbl-baseline
#| tbl-cap: Baseline characteristics of included data
web_data$table1
```

Here are the regression results.

```{r}
#| label: tbl-regression
#| tbl-cap: Regression analysis results
web_data$table2
```

## Discussion

Good luck on your further work!
